Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students

### 2024-02-15 paper/paper.qmd
Amended paper
Updated some of the information in the data section

To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline. We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares in each of the 21 states. From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years. From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through color, and year through shape.

@@

# Define quantiles for white share
white_share <- white_share |>
  group_by(state) |>
  mutate(quantile = ntile(share_enroll_white, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))

# Define quantiles for black share
black_share <- black_share |>
  group_by(state) |>
  mutate(quantile = ntile(share_enroll_black, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))

# Define quantiles for hispanic share
hispanic_share <- hispanic_share |>
  group_by(state) |>
  mutate(quantile = ntile(share_enroll_hispanic, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))

>>>>

To generate this graph, we once again employed the cleaned `scores_lm_demographics.csv` file as was used to generate @fig-mathscoresbyonline and @fig-elascoresbyonline. We first filtered by subject to only consider one at a time, after which the total enrollment across all school districts was calculated as well as the two quantiles, "Low" and "High", for each of the three races relative to the average shares across all school districts. From there, we grouped the data by year and quantile for each of the three races, then calculated the weighted average change in test pass rates for each subject and quantile, across all races and years. From there, we simply combined the summary statistics for each of the races and their respective quantiles, and showcased them in the figures, differentiating by race through color, and year through shape.

@@

# Define quantiles for white share
white_share <- white_share |>
  mutate(quantile = ntile(share_enroll_white, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))

# Define quantiles for black share
black_share <- black_share |>
  mutate(quantile = ntile(share_enroll_black, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))

# Define quantiles for hispanic share
hispanic_share <- hispanic_share |>
  mutate(quantile = ntile(share_enroll_hispanic, 2)) |>
  mutate(quantile_level = case_when(
    quantile == 1 ~ "Low",
    quantile == 2 ~ "High"
  ))
